Analysis of Water Security in Jordan

### 2022-04-03 outputs/paper/paper.Rmd
All but discussion completed.

  To compile the data set, the R language was used, [@citeR], along with the packages, Pointblank [@citepointblank], haven [@citehaven], the paper was compiled using Knitr [@citeknitr] and KableExtra[@citeakableExtra] packages. The table was acquired through the PDF document using the package PDFtools [@citepdftools]. Also made use of reshape2 [@citereshape2] in manipulating the data to creae plots.

@@

p + coord_flip()
```
\newpage

@@

Unsurprisingly the majority of natural water sources such as wells are being used by rural residents, making up 3.7% of all rural water sources compared to the 1.1% asmong urban residents. Also Springs are only used by rural residents, making up 2.3% of rural sources.

@@

As we can see both rural and urban residences can access water quite readily  in the country of Jordan.

>>>>

  To compile the data set, the R language was used[@citeR], along with the packages, Pointblank [@citepointblank], haven [@citehaven], the paper was compiled using Knitr [@citeknitr] and KableExtra[@citeakableExtra] packages. The table was acquired through the PDF document using the package PDFtools [@citepdftools]. Also made use of reshape2 [@citereshape2] in manipulating the data to creae plots.

@@

p + coord_flip()
```

@@

  Unsurprisingly the majority of natural water sources such as wells are being used by rural residents, making up 3.7% of all rural water sources compared to the 1.1% asmong urban residents. Also Springs are only used by rural residents, making up 2.3% of rural sources. The relatively large number of tanker truck sources for rural residents is somewhat surprising considering in many parts of the Western world the main alternative to piped water sources would presumably be a well. More information regarding this seemingly strange occurence is given in section \@ref(FirstPoint)

@@

  As we can see both rural and urban residences can access water quite readily  in the country of Jordan. With rural residents slightly trailing, though that's not unexpected.
